Slitasje og kjørespor

### 2023-01-23 DRAFT_slitasjeOgKjørespor.Rmd
test: Test 955 with ea_spread_dev()

<!-- ERROR with summarise = T -->
```{r}
summary_temp <- ea_spread(indicator_data = slitasje_data,
                         indicator = i_2020,
                         regions = HIA_regions,
                         groups = region_HIF,
                         summarise = TRUE)
```

>>>>

<!-- Check with updated ea_spread -->
```{r}
mySummary <- ea_spread(indicator_data = slitasje_data,
                         indicator = i_2020,
                         regions = HIA_regions,
                         groups = region_HIF,
                         summarise = TRUE)

```
